---
title: "README"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## shlr

This is an API client to retrieve data from the Swedish Hockey League Open API. 

To be able to use it you need to apply for a client id and client secret from http://doc.openapi.shl.se/.

When you have these you can save them as environmentvariables:

```{r eval=FALSE}
Sys.setenv('SHL_CLIENT_ID' = "xxxxxx")
Sys.setenv('SHL_CLIENT_SECRET' = "xxxxxxxx")
```

For example you can get the top 10 players of a team (or the whole league) using `get_top10_player_stats()`. 

```{r}
library(shlr)
get_top10_player_stats(season = "2017", team_id = "DIF")
```

You can aquire the same information but for only goalies with `get_top10_player_stats()`.

You can get all the games for a season with `get_games()`.

```{r}
get_games(season = "2018")
```

Active teams and meta information about the teams:

```{r}
get_teams()
```

The current standing in SHL:

```{r}
get_team_standing(season = "2018")
```

